Let $\mathsf{V}$ and $\mathsf{W}$ be vector spaces and
$\mathsf{T}\colon\mathsf{V} \to \mathsf{W}$ be linear.
\begin{enumerate}[(a)]
\item Prove that $\mathsf{T}$ is one-to-one if and only if
  $\mathsf{T}$ carries linearly independent subsets of $\mathsf{V}$
  onto linearly independent subsets of $\mathsf{W}$.
\item Suppose that $\mathsf{T}$ is one-to-one and that $S$ is a subset
  of $\mathsf{V}$. Prove that $S$ is linearly independent if and only
  if $\mathsf{T}(S)$ is linearly independent.
\item Suppose $\beta = \left\{v_1,v_2,\dots,v_n\right\}$ is a basis
  for $\mathsf{V}$ and $\mathsf{T}$ is one-to-one and onto. Prove that
  $\mathsf{T}(\beta) =
  \left\{\mathsf{T}(v_1),\mathsf{T}(v_2),\dots,\mathsf{T}(v_n)\right\}$
  is a basis for $\mathsf{W}$.
\end{enumerate}
\begin{enumerate}[(a)]
\item 
\textbf{Forward Direction:}
\\Suppose $S \subseteq \mathsf{V}$ such that  $S$ is linearly independent and
$\mathsf{T}$ is one-to-one.\\ Let $\mathsf{T}(S) = \{\mathsf{T}(x)
\colon x \in S\}$
\\Claim: $\mathsf{T}(S)$ is linearly independent.
\\Suppose $x \in \text{span}(\mathsf{T}(S))$ such that $ x = c_1u_1
+c_2u_2 + \cdots + c_nu_n =0$ for $c_i \in F$ and $u_i \in
\mathsf{T}(S)$
\paragraph{}
$\mathsf{T}$ is one-to-one $\implies u_i =\mathsf{T}(v_i)$ for some
unique $v_i \in S$
\begin{align}
\implies x &= c_1\mathsf{T}(v_1) +c_2\mathsf{T}(v_2) +\cdots +
c_n\mathsf{T}(v_n)\\
&= \mathsf{T}(c_1v_1 +c_2v_2 +\cdots+c_nv_n)\\
&= 0
\end{align}
\begin{equation}
\implies c_1v_1 + c_2v_2 +\cdots c_nv_n = 0
\end{equation}
\begin{equation}
\implies c_1=c_2=\cdots=c_n
\end{equation}
Therefore there only exists the trivial solution to the linear
combination $x$.

\textbf{Reverse Direction:}
Suppose $S\subseteq \mathsf{T}$ such that $S$ is linearly independent
and $\mathsf{T}(S)$ is linearly independent.
\\Claim: $\mathsf{T}$ is one-to-one
\\Suppose $x,y \in \text{span}(S)$ such that $x\neq y$ 
\begin{align}
x &= a_1u_1 + a_2u_2 + \cdots a_nu_n\\
y &= b_1u_1 + b_2u_2 + \cdots b_nu_n
\end{align}
Because $S$ is linearly independent each linear combination is
unique. 
\begin{equation}
\implies a_i \neq b_i\;\;\text{for some}\;\; i =1,2,\dots,n
\end{equation}
\begin{align}
\text{Let}\;\; \mathsf{T}(x) &= \mathsf{T}(a_1u_1 + a_2u_2 +\cdots
+a_nu_n)\\
\implies \mathsf{T}(x) &= a_1\mathsf{T}(u_1) + a_2\mathsf{T}(u_2)
+\cdots+a_n\mathsf{T}(u_n)\\
\text{Let}\;\; \mathsf{T}(y) &= \mathsf{T}(b_1u_1 + b_2u_2 +\cdots
+b_nu_n)\\
\implies \mathsf{T}(y) &= b_1\mathsf{T}(u_1) + b_2\mathsf{T}(u_2) +\cdots+b_n\mathsf{T}(u_n)
\end{align}
\begin{equation}
\mathsf{T}(u_i) \in \mathsf{T}(S) \forall i = 1,2,\dots,n
\end{equation}
\begin{equation}
\implies \mathsf{T}(x),\mathsf{T}(y) \in \text{span}(\mathsf{T}(S))
\end{equation}
Because $\mathsf{T}(S)$ is linearly independent each linear
combination is unique. 
\begin{equation}
\implies \mathsf{T}(x) \neq \mathsf{T}(y)
\end{equation} 
\newpage{}
\item 
Suppose $\mathsf{T}$ is one-to-one, $S \subseteq \mathsf{V}$
\\\textbf{Forward Direction:}
\\Suppose $S$ is linearly independent.
\\Claim $\mathsf{T}(S)$ is linearly independent.
\\$\mathsf{T}(S)$ is linearly independent by part (a)
\\\textbf{Reverse Direction:}
\\Suppose $S=\{v_1,v_2,\dots,v_m\}$
\begin{equation}
\implies \mathsf{T}(S) = \left\{\mathsf{T}(v_1) + \mathsf{T}(v_2)
  +\cdots+\mathsf{T}(v_m)\right\}
\end{equation}
Suppose $\mathsf{T}(S)$ is linearly independent.
\\Claim: $S$ is linearly independent.
\\Suppose $x \in \text{span}(S)$ such that $x = c_1v_1 + c_2v_2
+\cdots+c_mv_m = 0,\; c_i \in F$
\begin{align}
\implies \mathsf{T}(x) &= \mathsf{T}(c_1v_1+c_2v_n +\cdots+c_mv_m)\\
&= \mathsf{T}(0)\\
&= 0\;\;\text{(by theorem 2.4)}
\end{align}
\begin{equation}
\mathsf{T}(x) =c_1\mathsf{T}(v_1) + c_2\mathsf{T}(v_2)
+\cdots+c_m\mathsf{T}(v_m) =0
\end{equation}
\begin{equation}
\mathsf{T}(v_i)\in\mathsf{T}(S)\; \forall i=1,2,\dots,m
\end{equation}
Therefore $\mathsf{T}(x) \in \text{span}(\mathsf{T}(S))$ 

\begin{equation}
\mathsf{T}(S)\;\;\text{is linearly independent} \implies c_1=c_2=\cdots=c_m=0
\end{equation}
\item Suppose $\beta =\{v_1,v_2,\dots,v_n\}$ is a basis for
  $\mathsf{V}$ and $\mathsf{T}$ is one-to-one and onto.
\\Claim: $\mathsf{T}(\beta)$ is a basis for $\mathsf{W}$
\begin{align}
R\left(\mathsf{T}\right) &=\mathsf{W}\\
&= \text{span}\left(\mathsf{T}(\beta)\right) \text{(by theorem 2.2)}
\end{align}
$\mathsf{T}(\beta)$ is linearly independent by part (a)
\end{enumerate}
