If $(A\, | b)$ is in reduced row echelon form, prove that $A$ is
also in reduced row echelon form.

Suppose $(A\,|b)$ is an element of $\M{m}{(n+1)}{F}$ such that. $(A\,|b)$ is in row reduced echelon form.  To
complete this proof, it is necessary to show that $A$ satisfies the
definition of reduced row echelon form.

Claim $(A\,|b)$ in row reduced echelon form implies $A$ in row reduced echelon form

It is necessary to show that $A$ satisfies the definition of reduced
row echelon form.

\begin{enumerate}
\item Claim: any row of $A$ containing a nonzero entry precedes any row in
which all the entries are zero (if any)
\paragraph{Case 1:} The last column consists entirely of zeroes.
$(A\,|b)$ is in row reduced echelon form, so removing the last column still satisfies this
requirement

\paragraph{Case 2:} There is a nonzero value in the last column
Because there is a nonzero entry, it is the first nonzero entry of its
row.  However, it is in the last column position, and thus all other values in
the column are zero.  By property $C$ of the row reduced echelon form, all subsequent rows (if any)
must consist entirely of zeroes. 
Thus, the partition of the row reduced
echelon form of $(A\,|b)$ that
removes the last column yields matrix $A$ which satisfies this property.

\item Claim: The first nonzero entry in each row is the only nonzero entry in
its column. 

Removing the last column yields a matrix in which the first nonzero entry
in each row is the only nonzero entry in its column.

\item Claim:  The first nonzero entry in each row is 1 and it occurs in a
column to the right of the first nonzero entry in the preceding row.

\paragraph{Case 1:} The last column consists entirely of zeroes.
Thus, removing the last column from the row reduced echelon form of $(A\,|b)$ yields a matrix in which the
first nonzero entry in each row is 1 nd it occurs to the righ tof the
first nonzero entry in the preceding row.

\paragraph{Case 2:}  There is a non zero value in the last column
If there is a nonzero value in the last column, than that row consists
entirely of zeroes otherwise and all subsequent rows (if any) consist
entire of zeroes.  Thus, removing this column from the row reduced
echelon form of $(A\,|b)$ yields a
matrix that satisfies this property.
\end{enumerate}
